Analysis paper

### 2021-06-04 analysis/analysis.Rmd
update figures

scores_target <- eval_forecasts(
  filtered_data, 
  summarise_by = c("model", "target_type", "classification"), 
  compute_relative_skill = TRUE
)

>>>>

scores_target <- eval_forecasts(
  filtered_data[model %in% regular_models], 
  summarise_by = c("model", "target_type", "classification"), 
  compute_relative_skill = TRUE
)
